Probabilites of polar aligned disks in binary star systems

### 2024-03-11 src/tex/ms.tex
Add refs for gas and debris disks. Also fix spelling mistakes

% Abstract with filler text
\begin{abstract}
    Inclined circumbinary disks settle to one of three configurations: 1) prograde coplanar,
    2) retrograde coplanar, and 3) polar aligned. The preferred alignment can be found analytically
    in the case of a massless disk, however disk-star interactions make the general case much more challenging.
    We employ the N-body code REBOUND to investigate the dynamics of these 3-body systems and use monte-carlo methods
    to quantify the probabilities of the various configurations in a given system.
\end{abstract}

@@

Circumbinary planets -- those orbiting two stars -- have been mostly found to orbit in the same plane as
their hosts \citep{doyle2011,orosz2012,welsh2012}. However, \citet{aly2015} and \citet{martin2017} found that disks around eccentric binaries
can evolve to a polar state if their inclination is perturbed from coplanar. AC Her, a post-AGB system with a polar-inclined
disk, is believed to host the first circumbinary planet found in a polar orbit \citep{martin2023}.

>>>>

% Abstract with filler text
\begin{abstract}
    Inclined circumbinary disks settle to coplanar or polar-aligned configurations with respect to the binary host.
    The preferred alignment can be found analytically
    in the case of a massless disk, however disk-star interactions make the general case much more challenging.
    We employ the N-body code REBOUND to investigate the dynamics of these 3-body systems and use monte-carlo methods
    to quantify the probabilities of the various configurations in a given system.
\end{abstract}

@@

Circumbinary planets -- those orbiting two stars -- have been mostly found to orbit in the same plane as
their hosts \citep{doyle2011,orosz2012,welsh2012}. However, \citet{aly2015} and \citet{martin2017} found that disks around eccentric binaries
can evolve to a polar state if their inclination is perturbed from coplanar. A polar-aligned debris disk has been found in the 99 Her system
\citep{kennedy2012} and polar-aligned gas disks have been found in the HD 98800 and V773 Tau systems \citep[respectively]{kennedy2019,kenworthy2022}.
AC Her, a post-AGB system with a polar-inclined
disk, is believed to host the first circumbinary planet found in a polar orbit \citep{martin2023}.
